---
title: "Demo"
author: "Vas and Psych"
date: '2022-07-21'
output: html_document
---
Setup Packages Installation and Libraries
```{r}
#install.packages("bootnet")
#install.packages("networktools")
#install.packages("NetworkComparisonTest")
#install.packages("qgraph")
#install.packages("psych")
#install.packages("tidyverse")
#install.packages("semTools")
#install.packages("psychotools")
#install.packages("semPlot")
#install.packages("haven")
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)
library(psych)
library(psychotools)
library(tidyverse)
library(semTools)
library(semPlot)
library(haven)

```

Importing the data
```{r echo=FALSE, warning=FALSE, error=FALSE}
dataset <- read_sav("data.sav")
data<-read_sav("C:/Users/vasil/Desktop/Desktop 2022/PhDs/LizzieandFriends/useravatar/AvatarNetwork 2 months later/data.sav")
View(dataset)
# Look at the variables within the dataset 
names(dataset)
myvars <- c("Age", "Gender_New", "IGDTotal", "PON", "POF", "IDENT", "IMMERS","Compensation")
### subset data to run a network with desired variables.
## In this case I will look at columns 28-33
netweorkdata <- dataset %>%
  select(28:33)
names(netweorkdata)
#myvars2<-c("PON", "POF", "IDENT")
netdata <- dataset[myvars]
netdata1<-netdata[c(-2)]
netdata2<-netdata1[c(-1)]
view(netdata1)
view(netdata2)
#netdata3<-dataset[myvars2]
#describe(netdata3)
#netdata4<-netdata3[c(-2)]
describe(netdata)
describe(netdata1)
describe(netdata2)
#view(netdata3)
#describe(netdata4)
```
#A few words about Networks
1. Deegree/ Strength centrality= the number of links incident upon a node (i.e., the number of ties that a node has). The degree can be interpreted in terms of the immediate risk of a node for catching whatever is flowing through the network (such as a virus, or some information). 
In the case of a directed network (where ties have direction), we usually define two separate measures of degree centrality, namely indegree and outdegree. 
2. Closeness centrality (or closeness) of a node is the average length of the shortest path between the node and all other nodes in the graph. Thus the more central a node is, the closer it is to all other nodes.
3. Betweenness centrality quantifies the number of times a node acts as a bridge along the shortest path between two other nodes.
4. Eigenvector centrality (also called eigencentrality or expected influence) is a measure of the influence of a node in a network. It assigns relative scores to all
#Run Names if you don't have names in your dataset
```{r echo=FALSE, warning=FALSE, error=FALSE}
#names <- c("AGE", "GENDER", "INTERNET GAMING DISORDER", "PROTEUS EFFECT ONLINE", #"PROTEUS EFFECT OFFLINE", "IDENTIFICATION", "IMMERSION", "COMPENSATION")
#names1<- c("AGE","INTERNET GAMING DISORDER", "PROTEUS EFFECT ONLINE", "PROTEUS #EFFECT OFFLINE", "IDENTIFICATION", "IMMERSION", "COMPENSATION")
#names2 <-c("INTERNET GAMING DISORDER", "PROTEUS EFFECT ONLINE", "PROTEUS EFFECT #OFFLINE", "IDENTIFICATION", "IMMERSION", "COMPENSATION")
```

Estimate Network(s) with and without age 
```{r echo=FALSE, warning=FALSE, error=FALSE}
network1<-estimateNetwork(netdata1, default="EBICglasso")
## inspect the object to assess number of non-zero edges
network1
network2<- estimateNetwork(netdata2, default="EBICglasso")
## inspect the object to assess number of non-zero edges
network2
## you can also write an excel file with your regularized correlation matrix
## for subsequent analyses
Crmnet1 <-as.tibble(getWmat(network1))
view(Crmnet1)
names(Crmnet1)
describe(Crmnet1)
write_csv(Crmnet1, "reg correlation matrix 1.csv")
```
For Grouping Variables
Grouping nodes-if you need it
```{r echo=FALSE, warning=FALSE, error=FALSE}
#group Ptoteus (Avatar to Gamer effects) and (Gamer to Avatar Effects) nodes
groups2=list("IGD"=c(1),"AGE"=c(2:3), "GAE"=c(4:6))
#Mygroups <- list("IGD"=c(1),"AGE"=c(2:3), "GAE"=c(4:6)) 
```
Calculating with bootstraping the network
```{r echo=FALSE, error=FALSE, warning=FALSE}
#Default Bootstrapping
b1 <- bootnet(network2, boots=1000, statistics=c("strength", "expectedInfluence", "edge"))
#Case Dropping Bootstrapping
b2 <- bootnet(network2, boots=1000, type="case", statistics=c("strength", "expectedInfluence", "edge"))
```
```{r}

plot(network2, layout="spring", vsize=6, border.color="black", groups=groups2, color=c('lightblue','orange', 'red')) 

plot(b2, layout="spring", label.color="black", label.prop = 0.9,
     legend.cex = 0.5, font = 2, vsize = 4, groups=groups2, 
     color=c('lightblue', 'orange', 'red'))

```
```{r echo=FALSE, warning=FALSE, error=FALSE}

## Correlation stability coefficient and plot

crs<-corStability(b2)
view(crs)
write.csv(crs)
plot(b2, "all")

plot(b1, labels = F, order = "sample")

```


